% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{friggeri-cv}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\header{Edith  } { Darin}
{\qquad \qquad  \qquad  \qquad Demography, Bayesian statistics and Geospatial data science}


\fcolorbox{white}{gray}{\parbox{\dimexpr\textwidth-1\fboxsep-1\fboxrule}{ . }}
\begin{aside}
\textbf{Nationality}
French
\textbf{Current home}
Oxford, UK
\textbf{Website}
Personal \href{https://edarin.github.io/thatsme/}{\scriptsize\faIcon{external-link-alt}}
~
\section{Contact}
\textbf{E-mail}
edith.darin@\\protonmail.com
~
\section{Tech repo}
\textbf{Github}
\href{https://github.com/edarin}{edarin}
\textbf{OpenStreetMap}
\href{https://www.openstreetmap.org/user/edithdarin/history#map=5/22.938/11.470}{edithdarin}
~
\section{Programming}
\textbf{OS Preferences}
Windows
GNU/Linux
\textbf{Statistical Programming}
R (+++)
Python (++)
\textbf{Reporting}
Microsoft Office
Latex
R Markdown
R Shiny
~
\section{Languages}
\textbf{French} native
\textbf{English} fluent
\textbf{German} intermediate
\textbf{Italian} intermediate
~
\end{aside}
\section{Education}
\begin{entrylist}
\entry
{2025 - \\ 2022}
{PhD in Demography}
{University of Oxford, UK}
{Topic:\textit{Estimating subnational population sizes in data-scarce contexts}. Affiliated with the Max Planck Institute for Demographic Research.}
\entry
{2019 - \\ 2018}
{MSc in Applied GIS and Remote Sensing}
{University of Southampton, UK}
{Dissertation featured in a peer-reviewed article.}
\entry
{2018 - \\ 2015}
{MSc in Statistics and Economics}
{\\Paris Graduate School of Economics, Statistics and Finance (ENSAE), France}{Semesters abroad at Humbold University and Galatasaray University.}
\entry
{2014 - \\ 2013}
{Double Bachelor's Degree in Economics and Sociology}
{\\École Normale Supérieure de Cachan, Université Paris-I-Panthéon-Sorbonne, France}
{}
\end{entrylist}
\section{Working experiences}
\begin{entrylist}
\entry
{2026 - \\ 2024}
{Population Data Scientist}
{Demographic Unit, University of Oxford, UK}
{Nowcast monthly population displacement in war-struck Ukraine.
\textit{Methods:} Curate an automatised geospatial data pipeline from web scrapping. Develop a dashboard, an API and a PostgreSQL database in Docker containers. Model monthly population stocks and flows from mobile phone data.}
\entry
{2024 - \\ 2018}
{Research Fellow}
{WorldPop, University of Southampton, UK}
{\textit{Until 08/21 Specialist Research Technician}\\
Building statistical models to provide up-to-date, spatially complete population count in data-scarce contexts. Predict and map population with high spatial resolution at the grid cell.   Lead modeller for filling population gaps in censuses impacted by insecurity (Burkina Faso and Mali). Lead trainer on gridded population estimation to national statistics offices. \\
\textit{Methods:} Hierarchical Bayesian modelling combining survey data with geospatial covariates. Random-forest models for producing high-resolution population estimates. Grid-based spatial sampling design for household surveys.
}
\entry{2017}{Data Scientist Intern}{mVAM, UN World Food Program, Italy}{ 
Assessing food security from remote sensing and mobile data collection. Support mission for Mali Country Office. \textit{Methods:} Machine-learning based propensity score weighting in complex survey design.}
\entry{2016}{ Data Scientist Intern}{Etalab, Governmental Task Force for OpenData, France}{\emph{OpenFisca}: French tax and benefit system micro-simulation platform. Finalist of the Open Government Partnership Hackathon. }
\end{entrylist}

\section{Grants}
\begin{entrylist}
\entry
{2021}
{Mapping refugees with high spatial resolution}
{UNHCR: \$80 000}
{Co-I for developing methods to map refugees for survey purposes.}
\entry
{2022}
{Statistical population modelling for census support}
{UNFPA: \$30 000}
{Co-I for creating a population model with Brazil Statistics Office (IBGE).}
\end{entrylist}

\clearpage

\begin{noside}
\section{Academic outcomes}
\textbf{Peer-reviewed papers}
\begin{itemize}
\item  Tackling public health data gaps through Bayesian high-resolution population estimation: A case study of Kasaï-Oriental, Democratic Republic of the Congo. Boo G, \textbf{Darin, E.}, Chamberlain HR, Hosner R, Akilimali PK, et al., \textit{PLOS Global Public Health}, 5(9): e0005072, 2025 \href{https://doi.org/10.1371/journal.pgph.0005072}{\scriptsize\faIcon{external-link-alt}}

\item How Accurate Are High Resolution Settlement Maps at Predicting Population Counts in Data Scarce Settings?  \textbf{Darin, E.}, Kashyap, R. and Leasure, D.R. \textit{Population, Space and Place}, 31: e70083., 2025 \href{https://doi.org/10.1002/psp.70083}{\scriptsize\faIcon{external-link-alt}}

\item Mapping refugee populations at high-resolution by unlocking humanitarian administrative data, \textbf{Darin, E.}; Dicko D. H.;  Galal H.; Jimenez R.M.; Park H.;  Tatem A.J.; Qader S., \textit{Journal of International Humanitarian Action}, 2024 \href{https://doi.org/10.1186/s41018-024-00157-6}{\scriptsize\faIcon{external-link-alt}}

\item Building footprint data for countries in Africa: To what extent are existing data products comparable?, Chamberlain H. R.; \textbf{Darin, E.}; Adewole A. W.; Lazar A.; Tatem A.J., \textit{Computers, Environment and Urban Systems}, 2024, 102104, \href{https://doi.org/10.1016/j.compenvurbsys.2024.102104}{\scriptsize\faIcon{external-link-alt}}
\item The Population Seen from Space: When Satellite Images Come to the Rescue of the Census, \textbf{Darin, E.}; Kuépié M.; Bassinga H, Boo G., Tatem A.J.; \textit{Population}, 2022, 77:3, \href{https://doi.org/10.3917/popu.2203.0467}{\scriptsize\faIcon{external-link-alt}}
\item High-resolution population estimation using household survey data and building footprints, Boo, G; \textbf{Darin, E.}; Leasure, D.R.; Dooley, C.A.; Chamberlain, H.R., et al, \textit{Nature Communications}, 2022, 13:1,    \href{https://www.nature.com/articles/s41467-022-29094-x}{\scriptsize\faIcon{external-link-alt}}
\item The role of earth observation in an integrated deprived area mapping "system" for low-to-middle income countries, Kuffer, M.; Thomson, D.R.; Boo, G.; Mahabir, R.; Grippa, T.; Vanhuysse, S.; Engstrom, R.; Ndugwa, R.; Makau, J.; \textbf{Darin, E}.; de Albuquerque, J.P. and Kabaria, C, \textit{Remote Sensing}, 2020, 12, 982.    \href{https://www.mdpi.com/2072-4292/12/6/982}{\scriptsize\faIcon{external-link-alt}} 
\item A grid-based sample design framework for household surveys, Boo G; \textbf{Darin E}; Thomson DR and Tatem AJ, \textit{Gates Open Research} 2020, 4:13, \href{https://gatesopenresearch.org/articles/4-13/v1}{\scriptsize\faIcon{external-link-alt}}

\end{itemize}

\textbf{R Package}
\begin{itemize}
\item wopr: An R package to query the WorldPop Open Population Repository, version 1.0.1, Leasure DR; Bondarenko M; \textbf{Darin E}; Tatem AJ, \textit{WorldPop, University of Southampton}, 2020. Maintainer: \textbf{Darin E}. \href{https://apps.worldpop.org/woprVision/}{\scriptsize\faIcon{external-link-alt}}
\end{itemize}

\textbf{Recent conferences}
\begin{itemize}
\item Oral: Unraveling the Impact of the 2023 Conflict between Israel and Hamas on Short And Mid-Term Population Internal Displacements in the Middle East, \textbf{Darin E}, \textit{European Population Conference}, 2024.
\item Oral: Assessing Satellite Imagery Performance for Population Estimation in Data-Scarce Settings: A Modeling Perspective, \textbf{Darin E}, \textit{Population Association of America}, 2024.

%\item Oral: Estimating population in data-scarce contexts: to which extent can we leverage satellite imagery, \textbf{Darin E}, \textit{British Society of Population Studies}, 2023.

%\item Oral: Counting people from space: an inquiry from a data practitioner perspective, \textbf{Darin E}, \textit{Data Justice Conference}, 2023.
% \item Oral: A bottom-up population modelling approach to complement the population and housing census, \textbf{Darin E}; Boo G; Tatem AJ, \textit{International Population Conference}, 2021. \href{https://www.researchgate.net/publication/357017300_A_bottom-up_population_modelling_approach_to_complement_the_population_and_housing_census}{\scriptsize\faIcon{external-link-alt}}
% \item Poster: How Bayesian modelling could use the Big Tech competition in producing built-up maps, \textbf{Darin E}, \textit{Bayesian methods for the social sciences}, 2022.  \href{http://dx.doi.org/10.13140/RG.2.2.15592.55040}{\scriptsize\faIcon{external-link-alt}}
% \item Poster: High-resolution population mapping and estimation in the western part of the Democratic Republic of Congo, \textbf{Darin E}; Boo G;  Leasure DL and Tatem AJ, \textit{GEOMED 2019}, 2019.  \href{https://www.researchgate.net/publication/335320708_High-resolution_population_mapping_and_estimation_in_the_western_part_of_the_Democratic_Republic_of_Congo?channel=doi&linkId=5d5e587f299bf1b97cfd0ba7&showFulltext=true}{\scriptsize\faIcon{external-link-alt}}
\end{itemize}


\textbf{Teaching}
\begin{itemize}
\item Workshop: Gridded population modelling for Summer Institutes in Computational Social Science, Covenant, Nigeria 2022, Joseph Ki-Zerbo and Norbert Zongo University, Burkina Faso 2021, Data Science Nigeria Bootcamp 2019

\item  Tutorials: Statistical population modelling for census support; \textit{WorldPop, University of Southampton}, 2021, \href{https://wpgp.github.io/bottom-up-tutorial/}{\scriptsize\faIcon{external-link-alt}}. Small area population estimates using random forest top-down disaggregation: An R tutorial;   \textit{WorldPop, University of Southampton}, 2020. \href{https://htmlpreview.github.io/?https://github.com/wpgp/top-down-tutorial/blob/master/4_tutorial.html#Suggested_Citation}{\scriptsize\faIcon{external-link-alt}}.

\item R Foundations Course for different Nigerian national agencies, 2020. Population Modelling Webinar, \textit{GRID3 Webinar Series}, 2020. \href{https://www.youtube.com/watch?v=HMFM8HzLfH8}{\scriptsize\faIcon{external-link-alt}}

\end{itemize}


\section{Awards}
\begin{itemize}
\item Three-year scholarship from the Leverhulme Centre for Demographic Research (3x32,000), 2022
\item Faculty Dean's Prize for Research, University of Southampton, 2021
\item Vice-Chancellor Award for Research Impact, University of Southampton, 2018
\item Scholarship Sarah Andrieux for Social and Economics Research (800€), 2017
\item Four-year scholarship from the École Normale supérieure de Cachan (4x15,600€), 2015
\end{itemize}
\end{noside}

\end{document}
